r5r: Rapid Realistic Routing with R5 in R

### 2020-09-17 r-package/paper2020/paper2020.Rmd
removes tz argument from datetimes in examples

---
title: 'r5r: Rapid Realistic Routing with R5 in R'
author: "   "
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: " write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

@@

@@

```{r, message = FALSE}
mode <- c("WALK", "TRANSIT")
max_walk_dist <- Inf
max_trip_duration <- 120L
departure_datetime <- as.POSIXct("13-03-2019 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S",
                                 tz = "America/Sao_Paulo")

>>>>

---
title: 'r5r: Rapid Realistic Routing with R5 in R'
author: "   "
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: " write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

Test [@http://zotero.org/users/local/FtLgDWw9/items/8CHCA2S3]

@@

```{r, message = FALSE}
mode <- c("WALK", "TRANSIT")
max_walk_dist <- Inf
max_trip_duration <- 120L
departure_datetime <- as.POSIXct("13-03-2019 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")
